---
title       : Slides for Peer Assignment
subtitle    : Coursera Class Developing Data Products
author      : Peter
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Application to predict the mpg of your next car

> - Need to accurately predict mpg of next you purchase
> - Consumers request objective answers
> - Factory estimates not always honest?
> - Ease of use essential - see prototype

```{r fig.align='right', fig.width=10, fig.height=6, echo = F}
library(png)
library(grid)
img <- readPNG("./assets/img/James_and_Browne_car.png")
 grid.raster(img)
```

--- .class #id
## Where do we go from here?

 - Gather more and more accurate data
 - Create a model with multiple predictors
 - Design a mobile App with a web based back end
 - Develop other features to complement the mpg estimates
<br>
<br>
<br>


##                                                          Short Demo --->

--- .class #id 

## How to predict the MPG using cars weight:

```{r message = F, echo = T}
data(mtcars); library(caret)
mpg <- mtcars$mpg
weight <- mtcars$wt
lM <- lm(mpg ~ weight)
newdata <- data.frame(weight = 3)
p <- predict(lM, newdata, interval = "predict")
```
1. Load the data - mtcars
2. requires the caret package in R
3. Uses the linear regression model implemented in R by lm()
4. Create new dataframe with desired weigth (here in 1000 lbs)
5. Run prediction function with model

--- &twocol

## Sample Plot with Cars of various types ##

*** =left
<br>

```{r scplot, dev = 'png', fig.align='left', fig.width = 6.5, fig.height = 5, echo = F}
qplot(weight*1000,mpg)+ xlab("Car Weight") + ylab("Miles per Gallon") +
            stat_smooth(method="lm") + ggtitle( "Miles per Gallon vs car weight in lbs") +
            geom_pointrange(aes(x=3000, y=p[1,1], 
                            ymin=p[1,2], ymax=p[1,3]), size = 1, shape = 22, colour = "red")
```
*** =right
  <br>
  <br>
Print-out of an example estimating the MPG of a 
car with about 3000 lbs of dry weight:
<br>

```{r message = F, echo = F   }
p
```
<br>
fit = fitted value

lwr = lower end of prediction interval

upr = upper end of prediction interval
